\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip Air cleaners and respiratory infections in schools: \\ A modeling study using epidemiological, environmental, and molecular data}

### 2023-11-06 doc/paper/supplements.tex

Our estimation results imply a small, potential benefit of air cleaners. Subject to considerable uncertainty, \Cref{fig:avoided-infections} shows the estimated number number of infections that would have occurred if air cleaners had been installed throughout the study (scenario~1) or not been installed (scenario~2).

\begin{figure}[!htpb]
    \includegraphics{../../results/epi-data/avoided-infections.pdf}
    \caption[Estimated number of infections with and without air cleaners]{Estimated mean number of infections (posterior mean as dot and 50\%, 80\%, and 95\%-CrI as shaded areas) if, in both classes, air cleaners had been installed throughout the study or not been installed.}
    \label{fig:avoided-infections}
\end{figure}

>>>>

% Our estimation results imply a small, potential benefit of air cleaners. Subject to considerable uncertainty, \Cref{fig:avoided-infections} shows the estimated number number of infections that would have occurred if air cleaners had been installed throughout the study (scenario~1) or not been installed (scenario~2).

% \begin{figure}[!htpb]
%     \includegraphics{../../results/epi-data/avoided-infections.pdf}
%     \caption[Estimated number of infections with and without air cleaners]{Estimated mean number of infections (posterior mean as dot and 50\%, 80\%, and 95\%-CrI as shaded areas) if, in both classes, air cleaners had been installed throughout the study or not been installed.}
%     \label{fig:avoided-infections}
% \end{figure}
